Bird beak's elaboration and innovation

### 2022-04-25 Analysis/03-Elaboration_innovation_analysis.Rmd
Clade info for tree ploting

## Save all that as a list
save(ploting_data, file = "ploting_data.rda")
```

>>>>

## Save all that as a list
save(ploting_data, file = "ploting_data.rda")

## Group info
super_orders <- lapply(results$super_results_phylo$position$subsets, function(x, data) list(species = rownames(data)[c(x$elements)]), data = results$super_results_phylo$position$matrix[[1]])
orders <- lapply(results$order_results_phylo$position$subsets, function(x, data) list(species = rownames(data)[c(x$elements)]), data = results$order_results_phylo$position$matrix[[1]])
## Adding the colours
load("../Data/Processed/tip_colours_super_orders.rda")
load("../Data/Processed/tip_colours_orders.rda")
add.col <- function(one_order, one_col) {
    one_order$col <- one_col
    return(one_order)
}
super_orders <- mapply(add.col, one_order = super_orders[1:8], one_col = as.list(tip_colours_super_orders), SIMPLIFY = FALSE)
orders <- mapply(add.col, one_order = orders[1:27], one_col = as.list(tip_colours_orders), SIMPLIFY = FALSE)

## Big list:
clade_info <- list(super_orders = super_orders,
                   orders = orders)
## Save all that data
save(clade_info, file = "../Data/Processed/clade_info.rda")

## Get the names
names(clade_info$orders)

## Get the colours
unlist(lapply(clade_info$orders, `[[`, "col"))

## Get the species in one specific group
clade_info$orders$Cuculiformes$species

```
